Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating subgenome assignments in maize

### 2017-08-11 R/SubGenome Analysis.Rmd
Hardcoded support for windows file paths

---
title: "Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating subgenome assignments in maize"
output: html_document
params:
  fileParser: "../Perl/parseKsKnFile.pl"

@@

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/parseSubgenomes.R")
source("~/git/SubGenomes/R/addGOTerms.R")
```

>>>>

---
title: "Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating subgenome assignments in maize"
output: html_document
params:
  fileParser: "../Perl/parseKsKnFile.pl"
  goDataFile: "../Data/GO from maizecyc.tab"
  subGenomeFile: "/home/jesse/Dropbox/deleteme/outfile_processed_byHand.tab"

@@

```{r importSynMapData, include=FALSE}
## source("~/git/SubGenomes/R/parseSubgenomes.R")
## source("~/git/SubGenomes/R/addGOTerms.R")

source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
```
